### 2023-10-31 main.tex
^^
Remark...

		g_{k}(L,y_{k},c_{k},\ldots,c_{m})=\left(L+2-y_{k}-\sum_{i=k}^{m}c_{i}\right)^{c_{k}}

@@

		f(L,c_{1},\ldots,c_{m})=\frac{\Gamma(L+2-\sum_{i=1}^{m}c_{i})}{\Gamma(L+2)}

@@

\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi(\tau)

@@

\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\Psi^{'}(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)

@@

>>>>

		g_{k}(L,y_{k},c_{k},\ldots,c_{m})=\left(L+2-y_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}

@@

		f(L,c_{1},\ldots,c_{m})=\frac{\Gamma(L+2-\sum_{a=1}^{m}c_{a})}{\Gamma(L+2)}

@@

\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi(\tau)

@@

\begin{equation}\label{shorter-chain}
\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\Psi^{'}(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)

@@

\textbf{Remark}: Consider equation \eqref{shorter-chain} and the fact that, from equation \eqref{SteadyState-coeff-implicit} we have  
\Psi^{'}(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)=\Psi_{m}^{'}\left(s_{1},\ldots,s_{m}\right)=\Psi_{m}\left(s_{1},\ldots,s_{m}\right)
where $|\Psi_{m}^{'}\rangle$ and $|\Psi_{m}\rangle$ are the eigenvector with vanishing eigenvalues of a chain with length $m$. Therefore, we have that 
\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\Psi_{m}\left(s_{1},\ldots,s_{m}\right)
i.e., computing the $m$-point correlations is equivalent to computing the steady state of a chain of length $m$ where the occupations are $s_{1},\ldots,s_{m}$ and the coordinates of the sites are $y_{1},\ldots,y_{m}$. I still do not have an interpretation to this...
